Variational Monte Carlo on Bosonic Systems

### 2018-04-05 project_1/article/article.tex
Spell check one-body densities
        Also included is a reference to Jørgen.

    \subsection{One-Body Densities}
        % TODO: Fill in this part.
        % SEB: Sure thing, buddy
        In order to make some conclusion towards where the particles in our systems
        are most prone to exist, we need a good way to visualise our wavefunctions.
        It is impossible for a human being to visualise a probability density in three dimensions,
        because this measure would have to be represented in four dimensions. The fact that
        we will be studying systems of up to $n=500$ particles only adds to the headache.
        We therefore introduce the single-particle density function, or \emph{one-body density}
        $\rho(x, t)$. The one-body density is defined by the integral over all coordinates
        except one,
        \begin{align}
                \rho(x_1) \equiv \int \abs{\Psi(x_1, \dots, x_n)}^2 dx_2 \dots dx_n.
        \end{align}
        The one-body density can be interpreted as one-dimensional probability density for
        finding a particle in $x_1$-direction. We also have the following relation,
        \begin{align}
                n = \int \rho(x_1)dx_1,
        \end{align}
        in other words, the integral over the entire one-dimensional space in $x_1$-direction
        gives us the total number of particles in our system. This can be a bit odd at first sight
        as we are used to getting the number $1$ when we integrate over the entire density.

        It is best to think of the one-body density as the multivariate probability density
        for the entire system collapsed down to one dimension in a representation than looks very
        familiar to every physicist with a basic knowledge of quantum mechanics.

>>>>

    \subsection{One-Body Densities}
        In order to make some conclusion towards where the particles in our
        systems are most prone to exist, we need a good way to visualise our
        wavefunctions. If we are to visualize the combined wavefunction of two
        three-dimensional particles we need four dimensions per particle and can
        subtract one dimension as we look at a single probability density
        yielding a grand total of seven dimensions. The fact that we will be
        studying systems of up to $N = 500$ particles only adds to the headache.
        We therefore introduce the single-particle density function, or
        \emph{one-body density} $\rho(\vf{r})$. The one-body density is defined
        by the integral over all coordinates except one,
        \begin{align}
            \rho(\vf{r}_1)
            \equiv
            \int \dd\vf{r}_2 \dots \dd\vf{r}_N
            \abs{\Psi(\vf{r}_1, \dots, \vf{r}_N)}^2.
        \end{align}
        The one-body density represents the distribution of all the particles in
        the system. Furthermore, $\rho(\vf{r}_1)\dd\vf{r}_1$ will yield the
        probability of finding any particle within the volume element
        $\dd\vf{r}_1$. By convention the one-body density should be normalized
        such that the following relation holds,
        \begin{align}
            N = \int \rho(\vf{r}_1)\dd\vf{r}_1.
        \end{align}
        In other words, the integral over the entire volume in
        $\vf{r}_1$-direction gives us the total number of particles in our
        system. This can be a bit odd at first sight as we are used to getting
        unity when we integrate over the entire probability
        density.\cite{hogberget2013quantum}

        It is best to think of the one-body density as the multivariate
        probability density for the entire system collapsed down to one
        coordinate in a representation than looks very familiar to every
        physicist with a basic knowledge of quantum mechanics.
